%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Qiyu Zhi} % Your name
\address{247 Fitzpatrick hall\\ Notre Dame} % Your address
\address{South Bend \\ Indiana 46556} % Your secondary addess (optional)
\address{(574)~$\cdot$~386~$\cdot$~8935 \\ qzhi@nd.edu} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf University of Notre Dame} \hfill {\em Jan 2016 - Current} \\ 
Ph.D. in Computer Science \& Engineering

{\bf Beijing University of Posts and Telecommunications} \hfill {\em September 2011 - July 2015} \\ 
B.S. in Information Engineering 
\end{rSection}

%----------------------------------------------------------------------------------------
%	Publication SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Publications}
Gang Zhao, Ping Lu, Ruochen Xu, {\bf Qiyu Zhi}, and Ji Wu. Msiipl\_thu at tac2014 entity discovery and linking track. In Proc. Text Analysis Conference (TAC2014).

Qiuchi Li, {\bf Qiyu Zhi}, Miao Li, An combined sentiment classification system for SIGHAN-8, Association for Computational Linguistics (ACL) SIGHAN workshop.
\end{rSection}

%----------------------------------------------------------------------------------------
%	RESEARCH  INDUSTRY EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Research}

\begin{rSubsection}{Information Visualization Lab}{October 2015 - Present}{Research Assistant}{University of Notre Dame, IN}
\item Worked in area of Human Computer Interaction with an emphasis on Information Visualization. Built a domain custom keyboard to facilitate input.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Multimedia Signal \& Intelligent Information Processing Lab}{July 2014 - Auguest 2015}{Research Internship}{Tsinghua University, Beijing}
\item Worked on Chinese Weibo sentiment analysis, developed combined system for sentiment analysis, participated COAE and SIGHAN evaluation contest.
\item Participated in the entity linking track in KBP, TAC 2014. ranking 2/20. Devised a combined method to recognize entity.(base on java).recall ranking 2/20.
\item Worked on text summarization, especially on multi-documents summarization.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Network intelligence research center}{February 2014 - July 2014}{Research Internship}{Beijing University of Posts and Telecommunications, Beijing}
\item Developed a system to extract specific information from news material(base on C\#).
\item Proposed a Multi-type topic model (MTTM) to be used for Heterogeneous Information based on LDA.
\end{rSubsection}

\end{rSection}


\begin{rSection}{Industry}

\begin{rSubsection}{Tsinghua university - iflytek speech technology joint laboratory}{September 2014 - October 2014}{Software Engineering Intern}{Beijing, CHINA}
\item Participated in development of iflytek text search for speech System(base on python).\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{InceptionPad Inc.}{February 2013 - January 2014}{Web Developer}{Beijing, CHINA}
\item Developed incetionpad.com for BUPT entrepreneurship courses(base on PHP, javascript).
\end{rSubsection}


\end{rSection}


\begin{rSection}{Teaching}



\begin{rSubsection}{Operating System}{January 2016 - May 2016}{Teaching Assistant}{University of Notre Dame, IN}
\item Held office hours, graded projects.
\end{rSubsection}


\end{rSection}


%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{AWARDS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Excellent Graduation Thesis(50/854) & ~~~~~2015 \\
National Scholarship & ~~~~~2014,2015\\
Best Position Paper(Beijing Foreign Studies Univ. Model United Nation)  &  ~~~~~2014\\
Secretary of Sunshine Volunteer Association & ~~~~~2011,2012
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
